---
title: "6-LMEM"
output:
  word_document: default
  html_document: default
  pdf_document: default
date: "2023-04-26"
---

This Rmd conducts all inferential statistics and builds plots for Experiment 1.

# Set up

```{r setup, include=FALSE, echo=FALSE}

# clear workspace and load packages
rm(list=ls())
#setwd("./Documents/github/division-of-labor-analyses/exp_1")
source("../required_packages.R")
source("../libraries_and_functions.R")

#install.packages("pander")
library(pander)

# read in data
shuffled_data = read.table('./data/shuffled_mdrqa_and_conditions.csv', 
                  sep=',', header = TRUE)
real_data = read.table('./data/mdrqa_and_conditions.csv', 
                       sep=',', header = TRUE)
relphase_freq_data = read.table('./data/freq_tables-exp_1.csv', 
                                sep=',', header = TRUE)

# specify global plotting variables for TD: magma pallete
TD1 = "#fcfdbf"
TD2 = "#fc8961" 
TD3 = "#b73779"
TDcolors = c(TD1, TD2, TD3)
# specify global plotting variables for IE: viridis pallete
IE1 = "#fde725"
IE2 = "#21918c"
IE3 = "#3b528b"
IEcolors = c(IE1, IE2, IE3)

```

# Data preparation

```{r data-prep, echo=FALSE}

# add an indicator ("data") for real (.5) or surrogate (-.5) data ######
real_data$data <- "Real"
shuffled_data <- shuffled_data %>%
  mutate(data = "Surrogate") %>%
  mutate(DET = replace_na(DET, 0)) # fill in missing DET values

# specify variables to keep and bind the data
shared_variables = names(real_data)[names(real_data) %in% names(shuffled_data)]
shared_variables = shared_variables[c(4,17:20, 22:23)]
all_data = rbind.data.frame(dplyr::select(real_data,one_of(shared_variables)),
                                 dplyr::select(shuffled_data,one_of(shared_variables)))
real_data = select(real_data,one_of(shared_variables))

# Create factors and rename variables for nicer plots
real_data = real_data %>%
  mutate(dyad = as.factor(dyad)) %>%
  mutate(td_condition = as.factor(td_condition)) %>%
  mutate(ie_condition = as.factor(ie_condition)) %>%
  select(-c(data)) %>%
  rename(TD = td_condition) %>% 
  rename(IE = ie_condition) %>% 
  rename(Determinism = DET) %>% 
  rename(Time = timer) %>% 
  rename(Dyad = dyad) %>% 
  rename(Round = round_number)
all_data = all_data %>%
  mutate(dyad = as.factor(dyad)) %>%
  mutate(td_condition = as.factor(td_condition)) %>%
  mutate(ie_condition = as.factor(ie_condition)) %>%
  mutate(data = as.factor(data)) %>%
  rename(TD = td_condition) %>% 
  rename(IE = ie_condition) %>% 
  rename(Determinism = DET) %>% 
  rename(Time = timer) %>% 
  rename(Dyad = dyad) %>% 
  rename(Round = round_number) %>% 
  rename(Data = data)

```

## Hypothesis 1: More deterministic than chance.

### Model

```{r H1-model, echo=FALSE}

# construct the raw model
surrogate.model.raw = lmer(Determinism ~ 
                             # fixed effects
                             Data + 
                             # maximal random effect structure allowed
                             (1 | Dyad), # don't add into slope is not a fixed effect
                           data = all_data, REML = FALSE)
pander_lme(surrogate.model.raw,stats.caption = TRUE)
#tab_model(surrogate.model.raw)

# find residual DF for effect size calculation
summary(surrogate.model.raw) # df.resid is the way to go (it's more conservative here)
df.residual = df.residual(surrogate.model.raw)

# check out effect sizes for significant effects
t_to_eta2(t = c(108.536),
          df_error = c(df.residual)) 

# check out effect sizes
effectsizes_H1 <- as.data.frame(t_to_eta2(t = c(108.536),
                                          df_error = c(df.residual)))

# build the effect size table
colnames(effectsizes_H1) <- c("Partial Eta2", "CI", "CI Low" , "CI High" )
effectsizes_H1 <- effectsizes_H1 %>% mutate_if(is.numeric, round, digits=3) %>% 
  select(-CI) %>%
  mutate(Predictor = c("Data [Surrogate]")) %>%
  relocate(Predictor)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")
# build table
pander(effectsizes_H1, caption = "")

# save the H1 model
#tab_model(surrogate.model.raw, file = "./results/figures/exp_1-H1-LME_table.doc")

```

### Plots

```{r H1-plots, each=FALSE, echo=FALSE}

# specify global plotting variables for type of data: magma palette
real = "#fc8961"
surrogate = "#b73779" 

# create boxplot
ggplot(all_data, aes(x=Data, y=Determinism, fill = Data)) + 
  geom_boxplot(show.legend = FALSE) +
  #ggtitle("Determinism of Real vs. Surrogate Data") +
  theme_grey(base_size = 15) +
  scale_fill_manual(values = c(real, surrogate)) +
  xlab('Data Type') 
ggsave("./results/figures/exp_1-H1_plot.png")

```

## Hypothesis 2: Bi-directional task switching will result in faster completion times.

For this model, TD 1 is the equal task demand condition and IE 1 is the bidirectional switching condition. Given that these are the intended reference levels, the dummy coding by lme4 will suffice.

### Model

```{r H2-model, each=FALSE, echo=FALSE}

# check on normality of Time
shapiro.test(real_data$Time)
shapiro.test(log(real_data$Time)) # still not > .05, but more normal.
shapiro.test(scale(real_data$Time))

# take log of time
real_data <- real_data %>% mutate(Time = log(Time))

# raw model
completion.model.raw = lmer(Time ~ 
                              # fixed effects
                              TD*IE*Round + 
                              # random effects of dyad
                              (1 | Dyad),
                        data = real_data, REML = FALSE)
pander_lme(completion.model.raw,stats.caption = TRUE)
#tab_model(completion.model.raw)

# find residual DF for effect size calculation
anova(completion.model.raw) # gives DenDF - most conservative across effects
df.residual.td = 148.71
df.residual.td.ie = 148.44
df.residual.td.round = 150.81

# check out effect sizes
effectsizes_H2 <- as.data.frame(t_to_eta2(t = c(6.252, -2.629, -2.025),
          df_error = c(df.residual.td, df.residual.td.ie, df.residual.td.round)) )

# build the effect size table
colnames(effectsizes_H2) <- c("Partial Eta2", "CI", "CI Low" , "CI High" )
effectsizes_H2 <- effectsizes_H2 %>% mutate_if(is.numeric, round, digits=3) %>% 
  select(-CI) %>%
  mutate(Predictor = c("TD [2]", "TD [2] x IE [2]", "TD [3] x Round")) %>%
  relocate(Predictor)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")
# build table
pander(effectsizes_H2, caption = "")

```

### Post-hoc

```{r H2-posthoc, echo=FALSE}

# post-hoc of IE*TD2
posthoc.ie.td <- (emmeans(completion.model.raw, list(pairwise ~ TD*IE), adjust = "tukey"))[2]
posthoc.ie.td.df <- as.data.frame(posthoc.ie.td)
# add significance stars
stars <- as.data.frame(stars.pval(posthoc.ie.td.df[,6]))
posthoc.ie.td.df <- cbind(posthoc.ie.td.df, stars)
# rename columns
colnames(posthoc.ie.td.df) <- c("Pairwise Comparison", "Estimate", "Std. Error", "DF", "t-value", "Adjusted p-value", " ")
posthoc.ie.td.df <- posthoc.ie.td.df %>% mutate_if(is.numeric, round, digits=3)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(posthoc.ie.td.df, caption = "p < .10, * p < .05, ** p < .001")

```

### Plots

```{r H2-plots, each=FALSE, echo=FALSE}

# interaction between TD and IE
ggplot(real_data) +
  aes(x = TD, y = Time, fill = TD) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~IE, labeller = as_labeller(c("1"='IE 1', "2"='IE 2', "3"='IE 3'))) +
  scale_fill_manual(values = TDcolors) + # magma
  ggtitle("Impact of Task Demand and Individual Effectivities on Time") +
  theme_grey(base_size = 14) +
  ylab('Task Completion Time') +
  xlab('Task Demand')
ggsave("./results/figures/exp_1-H2-TDxIE.png", height = 5, width = 7)

# interaction between TD and Round
ggplot(real_data) +
  aes(x = as.factor(Round), y = Time, fill = as.factor(Round)) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~TD, labeller = as_labeller(c("1"='TD 1', "2"='TD 2', "3"='TD 3'))) +
  #scale_fill_viridis(discrete = TRUE, option = "rocket") +
  ggtitle("Impact of Task Demand and Round on Time") +
  theme_grey(base_size = 14) +
  labs(fill = "Round") +
  xlab('Round')  +
  ylab('Task Completion Time')
ggsave("./results/figures/exp_1-H2-TDxRound.png", height = 5, width = 7)

```

## Hypothesis 3: Bi-directional task switching leads to more time in relative coordination.

Once again, the reference levels are appropriately coded by the default dummy coding of lme4.

### Model 

```{r H3-model, each=FALSE, echo=FALSE}

# raw model
coordination.model.raw = lmer(Determinism ~ 
                            # fixed effects
                            TD*IE*Round + 
                            # random effects of dyad
                            (1 + TD | Dyad),
                        data = real_data, REML = FALSE)
pander_lme(coordination.model.raw,stats.caption = TRUE)
#tab_model(coordination.model.raw)
# save the H2 and H3 model as one
#tab_model(completion.model.raw, coordination.model.raw, file = "./results/figures/exp_1-H2_H3-LME_table.doc")

# find residual DF for effect size calculation
anova(coordination.model.raw) # gives DenDF
df.residual.td = 122.44

# check out effect sizes
effectsizes_H3 <- as.data.frame(t_to_eta2(t = c(2.275), 
                                          df_error = c(df.residual.td)))

# build the effect size table
colnames(effectsizes_H3) <- c("Partial Eta2", "CI", "CI Low" , "CI High" )
effectsizes_H3 <- effectsizes_H3 %>% mutate_if(is.numeric, round, digits=3) %>% 
  select(-CI) %>%
  mutate(Predictor = c("TD [2]")) %>%
  relocate(Predictor)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")
# build table
pander(effectsizes_H3, caption = "")

```

### Post-hoc

```{r H3-posthoc, echo=FALSE}

# post-hoc test of TD
posthoc.td <- emmeans(coordination.model.raw, list(pairwise ~ TD), adjust = "tukey")[2]
posthoc.td.df <- as.data.frame(posthoc.td)
# add significance stars
stars <- as.data.frame(stars.pval(posthoc.td.df[,6]))
posthoc.td.df <- cbind(posthoc.td.df, stars)
# rename columns
colnames(posthoc.td.df) <- c("Pairwise Comparison", "Estimate", "Std. Error", "DF", "t-value", "Adjusted p-value", " ")
posthoc.td.df <- posthoc.td.df %>% mutate_if(is.numeric, round, digits=3)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(posthoc.td.df, caption = "p < .10, * p < .05, ** p < .001")

```

### Plots

```{r H3-plots, each=FALSE, echo=FALSE}

# effect of TD
ggplot(real_data, aes(x=TD, y=Determinism, fill = TD)) + 
  geom_boxplot(show.legend = FALSE) +
  scale_fill_manual(values = TDcolors) +
  ggtitle("Impact of Task Demand on Relative Coordination") +
  theme_grey(base_size = 14) +
  xlab('Task Demand')
ggsave("./results/figures/exp_1-H3-TD.png", height = 5, width = 7)

```

## Hypothesis 4: In I.E. condition 2, P2 will adapt to (follow) P1

Once again, the reference levels are appropriately coded by the default dummy coding of lme4.

### Prepare data

```{r prepare-data, each=FALSE, echo=FALSE}
# create orthogonal polynomials for determining leading-following (first-order) and sychrony (second-order).
raw_relphase = min(relphase_freq_data$Var1):max(relphase_freq_data$Var1)
relphase_vals = data.frame(raw_relphase)
phase_offset = (0-min(raw_relphase)) + 1
t = stats::poly((raw_relphase + phase_offset), 2)
relphase_vals[, paste("ot", 1:2, sep="")] = t[relphase_vals$raw_relphase + phase_offset, 1:2]

# join it to the original data table
relphase_freq_data = left_join(relphase_freq_data,relphase_vals, by = c("Var1" = "raw_relphase"))

# explore the distribution of frequency to select appropriate normalization (contains 0 values)
freq_transforms <- relphase_freq_data %>% 
  rename(freq_raw = Freq) %>%
  mutate(freq_plus_1 = freq_raw + 1) %>%
  mutate(freq_scaled = scale(freq_raw))

# visualize hist and Q-Q for raw values
hist(freq_transforms$freq_raw, breaks = 1400, xlim = c(0,100))
qqnorm(freq_transforms$freq_raw, pch = 1, frame = FALSE)
qqline(freq_transforms$freq_raw, col = "steelblue", lwd = 2)
# visualize hist and Q-Q for log transformed raw time series with zeros (for comparison with other methods)
hist(log(freq_transforms$freq_raw), breaks = 30, xlim = c(0,7))
qqnorm(log(freq_transforms$freq_raw), pch = 1, frame = FALSE, ylim = c(0, 10))
qqline(log(freq_transforms$freq_raw), col = "steelblue", lwd = 2)
# visualize hist and Q-Q for log(x+1)
hist(log(freq_transforms$freq_plus_1), breaks = 30, xlim = c(0,7))
qqnorm(log(freq_transforms$freq_plus_1), pch = 1, frame = FALSE, ylim = c(0, 10))
qqline(log(freq_transforms$freq_plus_1), col = "steelblue", lwd = 2)
# visualize hist and Q-Q for scaled values
hist(freq_transforms$freq_scaled, breaks = 1400, xlim = c(0,2))
qqnorm(freq_transforms$freq_scaled, pch = 1, frame = FALSE, ylim = c(0, 10))
qqline(freq_transforms$freq_scaled, col = "steelblue", lwd = 2)

# create factors and rename variables
relphase_freq_data_raw = relphase_freq_data %>% ungroup() %>%
  mutate(dyad = as.factor(dyad)) %>%
  mutate(td_condition = as.factor(td_condition)) %>%
  mutate(ie_condition = as.factor(ie_condition)) %>%
  # scale ot1, ot2, and round and log(x+1) transform frequency
  rename(rawFreq = Freq) %>%
  mutate(logFreq = log(rawFreq+1)) %>%
  mutate(ot1 = scale(ot1)) %>%
  mutate(ot2 = scale(ot2)) %>%
  mutate(round = scale(round)) %>%
  rename(TD = td_condition) %>% 
  rename(IE = ie_condition) %>% 
  rename(Dyad = dyad) %>% 
  rename(Round = round) %>% 
  #rename(Frequency = Freq) %>% 
  rename(RelativePhase = Var1) %>%
  mutate(RelativePhase = as.factor(RelativePhase))

```

### Model

```{r H4-model, each=FALSE, echo=FALSE}

# raw model
relphase.gca.raw = lmer(logFreq ~ 
                          # fixed effects
                          #Round +
                          TD*IE*ot1*ot2*Round +
                          # random effect
                          (1 + ot1 | Dyad),
                        data=relphase_freq_data_raw, REML=FALSE)
pander_lme(relphase.gca.raw,stats.caption = TRUE)
#tab_model(relphase.gca.raw)

# find residual DF for effect size calculation
anova(relphase.gca.raw) # gives DenDF
summary(relphase.gca.raw)
df.resid = 57323

# check out effect sizes
effectsizes_H4 <- as.data.frame(t_to_eta2(t = c(8.652, -2.716, -4.831, -2.277, -2.903,
                                                5.115, -2.14, 1.985, -2.264, -1.992,
                                                -5.307, -3.098, -3.406, 2.353, 3.351,
                                                2.036, -2.017, -2.346, -2.279, 4.379,
                                                3.785, 5.732, 3.531, 2.854, 2.925,
                                                2.585, -4.37, -5.164, -2.659, -2.715,
                                                -5.035, -2.711, 2.156),
                                              df_error = c(df.resid,df.resid,df.resid,
                                                           df.resid,df.resid,df.resid,
                                                           df.resid,df.resid,df.resid,
                                                           df.resid,df.resid,df.resid,
                                                           df.resid,df.resid,df.resid,
                                                           df.resid,df.resid,df.resid,
                                                           df.resid,df.resid,df.resid,
                                                           df.resid,df.resid,df.resid,
                                                           df.resid,df.resid,df.resid,
                                                           df.resid,df.resid,df.resid,
                                                           df.resid,df.resid,df.resid)))

# build the effect size table
colnames(effectsizes_H4) <- c("Partial Eta2", "CI", "CI Low" , "CI High" )
effectsizes_H4 <- effectsizes_H4 %>% mutate_if(is.numeric, round, digits=4) %>% 
  select(-CI) %>%
  mutate(Predictor = c("TD2","TD2:IE2","TD2:IE3","TD3:IE3","TD2:ot1", 
                       "TD3:ot1", "TD3:ot2", "IE2:ot2", "ot1:ot2", "TD2:Round",
                       "TD3:Round", "TD3:IE2:ot1", "TD2:IE3:ot1", "TD3:IE3:ot1", "TD2:IE2:ot2", 
                       "TD3:IE2:ot2", "TD3:ot1:ot2", "IE2:ot1:ot2", "IE3:ot1:ot2", "TD3:IE2:Round", 
                       "TD3:IE3:Round", "TD3:ot1:Round", "IE2:ot1:Round", "IE2:ot2:Round", "IE3:ot2:Round",
                       "TD2:IE3:ot1:ot2", "TD2:IE2:ot1:Round", "TD3:IE2:ot1:Round", "TD2:IE2:ot2:Round",
                       "TD3:IE2:ot2:Round", "TD3:IE3:ot2:Round", "TD3:ot1:ot2:Round", "TD3:IE2:ot1:ot2:Round")) %>%
  relocate(Predictor)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('round', 4)
# style for Rmd
panderOptions("table.style", "rmarkdown")
# build table
pander(effectsizes_H4, caption = "")

```

### Post-hoc

```{r H4-posthoc, echo=FALSE}

# visualize the regression lines
# emmip(relphase.gca.raw, IE ~ ot2, cov.reduce = range) +
#    scale_color_manual(values=IEcolors)
# ggsave('./results/figures/exp_1-H4-regression_IE_ot1.png') 

# post-hoc of TD*ot2
posthoc.td.ie.ot2 <- emtrends(relphase.gca.raw, ~TD*IE, var = "ot2")
posthoc.td.ie.ot2.df <- as.data.frame(pairs(posthoc.td.ie.ot2))
# add significance stars
stars <- as.data.frame(stars.pval(posthoc.td.ie.ot2.df[,6]))
posthoc.td.ie.ot2.df <- cbind(posthoc.td.ie.ot2.df, stars)
# rename columns
colnames(posthoc.td.ie.ot2.df) <- c("Pairwise Comparison", "Estimate", "Std. Error", "DF", "t-value", "Adjusted p-value", " ")
posthoc.td.ie.ot2.df <- posthoc.td.ie.ot2.df %>% mutate_if(is.numeric, round, digits=3) %>%
  select(-DF)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(posthoc.td.ie.ot2.df, caption = "p < .10, * p < .05, ** p < .001")

```

### Plots

```{r H4-hist-plots, each=FALSE, echo=FALSE}

# read in non-accumulated relative phase data
data <- read.csv("./data/data_prepped-exp_1.csv")
data <- data %>%
  tidyr::drop_na(rel_phase) %>%
  mutate(rel_phase_rescale = case_when(rel_phase > 180 ~ rel_phase-360,
                                       rel_phase < -180 ~ rel_phase+360,
                                       rel_phase <= 180 & rel_phase >= -180 ~ rel_phase)) %>%
  # round to the nearest degree
  mutate(rel_phase_rounded = round(rel_phase_rescale, digits = 0)) %>%

  # rename
  rename(TD = td_condition) %>%
  rename(IE = ie_condition) %>%
  rename(Dyad = dyad) %>%
  rename(Round = round_number) %>%
  mutate(TD = as.factor(TD)) %>%
  mutate(IE = as.factor(IE)) %>%
  mutate(Dyad = as.factor(Dyad)) %>%
  mutate(Round = as.factor(Round)) 
  #mutate(rel_phase_rounded = as.factor(rel_phase_rounded))

# # plot by dyad (IE 1)
# ggplot(data, aes(x = rel_phase_rounded, fill = IE)) + 
#   geom_histogram(binwidth = 8, color = "black", show.legend = FALSE) +
#   facet_wrap(~as.numeric(Dyad)) +
#   scale_fill_manual(values = IEcolors, name = "IE") +
#   xlab('Relative Phase') +
#   ylab('Frequency') +
#   ggtitle("Frequency of Relative Phase by Dyad (IE 1)") +
#   ggforce::facet_wrap_paginate(~ IE:Dyad, nrow = 3, ncol = 3, 
#                                page = 1, labeller = labeller('IE:Dyad' = c('1:1'="Dyad 1", 
#                                                                             '1:3'="Dyad 3", 
#                                                                             '1:5'="Dyad 5", 
#                                                                             '1:8'="Dyad 8", 
#                                                                             '1:10'="Dyad 10", 
#                                                                             '1:14'="Dyad 14", 
#                                                                             '1:15'="Dyad 15", 
#                                                                             '1:18'="Dyad 18", 
#                                                                             '1:21'="Dyad 21"))) +
#   theme_grey(base_size = 15) +
#   scale_x_continuous(breaks=c(-180,0,180))
# ggsave('./results/figures/exp_1-H4-dyad_hist_IE1.png', height = 5, width = 7)
# 
# # plot by dyad (IE 2)
# ggplot(data, aes(x = rel_phase_rounded, fill = IE)) + 
#   geom_histogram(binwidth = 8, color = "black", show.legend = FALSE) +
#   facet_wrap(~as.numeric(Dyad)) +
#   scale_fill_manual(values = IEcolors, name = "IE") +
#   xlab('Relative Phase') +
#   ylab('Frequency') +
#   ggtitle("Frequency of Relative Phase by Dyad (IE 2)") +
#   ggforce::facet_wrap_paginate(~ IE:Dyad, nrow = 3, ncol = 3, 
#                                page = 2, labeller = labeller('IE:Dyad' = c('2:9'="Dyad 9", 
#                                                                             '2:12'="Dyad 12", 
#                                                                             '2:16'="Dyad 16", 
#                                                                             '2:17'="Dyad 17", 
#                                                                             '2:19'="Dyad 19", 
#                                                                             '2:22'="Dyad 22", 
#                                                                             '2:24'="Dyad 24", 
#                                                                             '2:27'="Dyad 27", 
#                                                                             '2:31'="Dyad 31"))) +
#   theme_grey(base_size = 15) +
#   scale_x_continuous(breaks=c(-180,0,180))
# ggsave('./results/figures/exp_1-H4-dyad_hist_IE2.png', height = 5, width = 7)
# 
# # plot by dyad (IE 3)
# ggplot(data, aes(x = rel_phase_rounded, fill = IE)) + 
#   geom_histogram(binwidth = 8, color = "black", show.legend = FALSE) +
#   facet_wrap(~as.numeric(Dyad)) +
#   scale_fill_manual(values = IEcolors, name = "IE") +
#   xlab('Relative Phase') +
#   ylab('Frequency') +
#   ggtitle("Frequency of Relative Phase by Dyad (IE 3)") +
#   ggforce::facet_wrap_paginate(~ IE:Dyad, nrow = 3, 
#                                ncol = 3, page = 3, 
#                                labeller = labeller('IE:Dyad' = c('3:2'="Dyad 2", 
#                                                                   '3:4'="Dyad 4", 
#                                                                   '3:6'="Dyad 6", 
#                                                                   '3:7'="Dyad 7", 
#                                                                   '3:11'="Dyad 11", 
#                                                                   '3:13'="Dyad 13", 
#                                                                   '3:20'="Dyad 20", 
#                                                                   '3:23'="Dyad 23", 
#                                                                   '3:26'="Dyad 26"))) +
#   theme_grey(base_size = 15) +
#   scale_x_continuous(breaks=c(-180,0,180))
# ggsave('./results/figures/exp_1-H4-dyad_hist_IE3.png', height = 5, width = 7)
# 
# # plot histograms by IE collapsed across dyads
# ggplot(data, aes(x = rel_phase_rounded, fill = IE)) + 
#   geom_histogram(binwidth = 5, color = "black", show.legend = FALSE) +
#   facet_wrap(~as.numeric(IE), labeller = as_labeller(c("1"='IE 1', "2"='IE 2', "3"='IE 3'))) +
#   scale_fill_manual(values = IEcolors, name = "IE") +
#   xlab('Relative Phase') +
#   ylab('Frequency') +
#   ggtitle("Frequency of Relative Phase by IE Condition") +
#   theme_grey(base_size = 15) +
#   scale_x_continuous(breaks=c(-180,0,180))
# ggsave('./results/figures/H4-histogram_IE_collapsed.png', height = 5, width = 7)
# 
# # plot histograms by TD collapsed across dyads
# ggplot(data, aes(x = rel_phase_rounded, fill = TD)) + 
#   geom_histogram(binwidth = 5, color = "black", show.legend = FALSE) +
#   facet_wrap(~as.numeric(TD), labeller = as_labeller(c("1"='TD 1', "2"='TD 2', "3"='TD 3'))) +
#   scale_fill_manual(values = TDcolors, name = "TD") +
#   xlab('Relative Phase') +
#   ylab('Frequency') +
#   ggtitle("Frequency of Relative Phase by TD Condition") +
#   theme_grey(base_size = 15) +
#   scale_x_continuous(breaks=c(-180,0,180))
# ggsave('./results/figures/H4-histogram_TD_collapsed.png', height = 5, width = 7)

# plot histograms by TD*IE collapsed across dyads
ggplot(data, aes(x = rel_phase_rounded, fill = IE)) + 
  geom_histogram(binwidth = 5, color = "black", show.legend = FALSE) +
  facet_grid(TD~IE, labeller = labeller(TD = c('1'="TD 1", '2'="TD 2", '3'="TD 3"), 
                                        IE = c('1'="IE 1", '2'="IE 2", '3'="IE 3"))) +
  scale_fill_manual(values = IEcolors) +
  xlab('Relative Phase') +
  ylab('Frequency') +
  ggtitle("Frequency of Relative Phase by TD and IE") +
  theme_grey(base_size = 15) +
  scale_x_continuous(breaks=c(-180,0,180))
ggsave('./results/figures/H4-histogram_TD*IE_collapsed.png', height = 5, width = 7)

```