---
title: "6-LMEM"
output:
  word_document: default
  html_document: default
date: "2023-04-26"
---

This Rmd runs inferential statistics and builds plots for Experiment 3.

# Set up

```{r setup, include=FALSE}

# clear workspace and load packages
rm(list=ls())
#setwd("./Documents/github/division-of-labor-analyses/exp_3")
source("../required_packages.R")
source("../libraries_and_functions.R")

# read in data
data <- read.csv("./data/data_prepped-exp_3.csv")
mdrqa_results <- read.csv("./data/mdrqa_and_conditions.csv")

# specify global plotting variables for TD: magma pallete
TD1 = "#fcfdbf"
TD2 = "#fc8961" 
TD3 = "#b73779"
TDcolors = c(TD1, TD2, TD3)
# specify global plotting variables for IE: viridis pallete
IE1 = "#fde725"
IE2 = "#21918c"
IE3 = "#3b528b"
IEcolors = c(IE1, IE2, IE3)
# specify global plotting variables for COM
COM1 = "#0d0887"
COM2 = "#7e03a8"
COM3 = "#cc4778"
COMcolors = c(COM1, COM2, COM3)

# change conditions and dyads to be factors
data <- data %>%
  mutate(TD = as.factor(td_condition)) %>%
  mutate(IE = as.factor(ie_condition)) %>%
  mutate(COM = as.factor(com_condition)) %>%
  mutate(Dyad = as.factor(dyad)) %>%
  mutate(Round = round_number) %>%
  mutate(Time = timer)
  
# change contrasts for COM such that COM2 is the reference condition
contrasts(data$COM) = contr.treatment(3, base = 2)

## filter data in wide format for synchrony analyses
wide_raw <- data %>%
  distinct(Dyad, Round, IE, TD, 
           COM, Time, deg_sync_free, deg_sync_free2, 
           deg_sync_restrict, deg_sync_restrict2, mean_team_sync) %>%
  # remove the observations for before someone started moving
  drop_na(deg_sync_free, deg_sync_free2, deg_sync_restrict, deg_sync_restrict2, mean_team_sync) %>%
  mutate(Time2 = Time)# keep raw time as a separate variable for plotting

# restructure data and create player type indicator for player-team analyses
long_raw <- gather(wide_raw, player, deg_player_sync, deg_sync_free:deg_sync_restrict2)
long_raw$PlayerType <- as.factor(ifelse(long_raw$player == "deg_sync_free" | long_raw$player == "deg_sync_free2", 2, 1))
long_raw <- long_raw %>% mutate(Round2 = Round) %>% mutate(Round = scale(Round))
# add factors and rename variables for H1-H4
mdrqa_raw = mdrqa_results %>%
  mutate(Dyad = as.factor(dyad)) %>%
  mutate(TD = as.factor(td_condition)) %>%
  mutate(IE = as.factor(ie_condition)) %>%
  mutate(COM = as.factor(com_condition)) %>%
  mutate(Time2 = timer) %>% # keep raw time as a separate variable for plotting
  rename(Time = timer) %>% # use Time to be log transformed
  rename(Determinism = DET) %>%
  rename(Round = round_number)
contrasts(mdrqa_raw$COM) = contr.treatment(3, base = 2)

```

## Hypothesis 1-3: 
(1) Dyads in the restricted communication condition (COM2) will perform better than those in the no and free communication groups.
(2) Dyads in the no (COM1) and free (COM3) communication groups will perform similarly. 
(3) Dyads in the restricted communication (COM2) and bi-directional task switching condition (IE1) will outperform all other groups.

### Model 

```{r H1-H3-model, echo=FALSE}

###### 2. Construct the model for H1-H3 ######

# check on normality of Time
shapiro.test(mdrqa_raw$Time)
shapiro.test(log(mdrqa_raw$Time)) # still not > .05, but more normal.
shapiro.test(scale(mdrqa_raw$Time))

# take log of time
mdrqa_raw <- mdrqa_raw %>%
  mutate(Time2 = Time) %>%
  mutate(Time = log(Time))

# raw model
completion.model.raw = lmer(Time ~ 
                              # fixed effects
                              TD*IE*COM*Round +
                              # random effects of dyad
                              (1 | dyad),
                            data = mdrqa_raw, REML = FALSE)
pander_lme(completion.model.raw,stats.caption = TRUE)
#tab_model(completion.model.raw)

# find residual DF for effect size calculation
summary(completion.model.raw) # df.resid
df.residual = df.residual(completion.model.raw)

# check out effect sizes
effectsizes_H1_H3 <- as.data.frame(t_to_eta2(t = c(2.721, 2.583, -3.162, -1.993, -2.257,
                                                   -2.461, -2.000, -2.145, -2.697, -2.077,
                                                    2.297, 3.288, 14.946,  2.588, 3.696,
                                                   2.246, 2.791, -2.434,  -3.354, -11.764, -2.530),
                                          df_error = c(df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual)))

# build the effect size table
colnames(effectsizes_H1_H3) <- c("Partial Eta2", "CI", "CI Low" , "CI High" )
effectsizes_H1_H3 <- effectsizes_H1_H3 %>% mutate_if(is.numeric, round, digits=3) %>%
  select(-CI) %>%
  mutate(Predictor = c("TD2","COM1", "TD2:COM1", "TD3:COM1", "TD2:COM3", 
                       "IE3:COM1", "IE3:COM3", "TD2:Round", "COM1:Round", "COM3:Round",
                       "TD2:IE2:COM1", "TD2:IE3:COM1", "TD3:COM3:COM1","TD2:COM3:COM3", 
                       "TD2:COM1:Round","TD3:COM1:Round","TD2:COM3:Round","TD2:IE2:COM1:Round",
                       "TD2:IE3:COM1:Round","TD3:IE3:COM1:Round", "TD2:IE3:COM3:Round")) %>%
  relocate(Predictor)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")
# build table
pander(effectsizes_H1_H3, caption = "")

```

### Plots

```{r H1-H3-plots, each=FALSE, echo=FALSE}

# effect of COM (H1 and H2)
ggplot(mdrqa_raw) +
  aes(x=COM, y=Time2, fill = COM) + 
  geom_boxplot(show.legend = FALSE) +
  scale_fill_manual(values = COMcolors) +
  ggtitle("Impact of Communication on Time") +
  theme_grey(base_size = 14) +
  xlab('Communication') +
  ylab('Task Completion Time')
ggsave("./results/figures/exp_3-H1-H3-plot_COM.png", height = 5, width = 7)

# # effect of IE and COM (H3)
# ggplot(mdrqa_raw) +
#   aes(x = IE, y = Time2, fill = IE) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
#   scale_fill_manual(values = IEcolors) + # magma
#   #ggtitle("Impact of Task Demand and Individual Effectivities on Time") +
#   theme_grey(base_size = 14) +
#   xlab('Individual Effectivities')
# ggsave("./results/figures/exp_3-H1-H3-plot_IExCOM.png", height = 5, width = 7)
# 
# # effect of TD
# ggplot(mdrqa_raw) +
#   aes(x=TD, y=Time2, fill = TD) + 
#   geom_boxplot(show.legend = FALSE) +
#   scale_fill_manual(values = TDcolors) +
#   ggtitle("Impact of TD on Time") +
#   theme_grey(base_size = 14) +
#   xlab('Task Demand')
# ggsave("./results/figures/exp_3-H1-H3-plot_TD.png")
# 
# # interaction between TD and COM
# ggplot(mdrqa_raw) +
#   aes(x = TD, y = Time2, fill = TD) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
#   scale_fill_manual(values = TDcolors) + # magma
#   ggtitle("Impact of Task Demand and Communication on Time") +
#   theme_grey(base_size = 14) +
#   xlab('Task Demand')
# ggsave("./results/figures/exp_3-H1-H3-plot_TDxCOM.png")

# interaction between TD and IE
ggplot(mdrqa_raw) +
  aes(x = TD, y = Time2, fill = TD) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~IE, labeller = as_labeller(c("1"='IE 1', "2"='IE 2', "3"='IE 3'))) +
  scale_fill_manual(values = TDcolors) + # magma
  ggtitle("Impact of Task Demand and Individual Effectivities on Time") +
  theme_grey(base_size = 14) +
  xlab('Task Demand') +
  ylab('Task Completion Time')
ggsave("./results/figures/exp_3-H1-H3-plot_TDxIE.png", height = 5, width = 7)

# # interaction between TD, IE, and COM
# ggplot(mdrqa_raw) +
#   aes(x = TD, y = Time2, fill = TD) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_grid(COM~IE, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"), IE = c('1'="IE 1", '2'="IE 2", '3'="IE 3"))) +
#   scale_fill_manual(values = TDcolors) + # magma
#   ggtitle("Impact of TD, IE, and COM on Time") +
#   theme_grey(base_size = 14) +
#   xlab('Task Demand')
# ggsave("./results/figures/exp_3-H1-H3-plot_TDxIEXCOM.png")
# 
# # interaction between TD, COM, and Round
# ggplot(mdrqa_raw) +
#   aes(x = as.factor(Round), y = Time, fill = as.factor(Round)) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_grid(COM~TD, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"), TD = c('1'="TD 1", '2'="TD 2", '3'="TD 3"))) +
#   #scale_fill_manual(values = IEcolors) + # magma
#   ggtitle("Impact of TD, COM, and Round on Time") +
#   theme_grey(base_size = 14) +
#   xlab('Round')
# ggsave("./results/figures/exp_3-H1-H3-plot_TDxCOMxRound.png")

# plot histogram of Time
ggplot(mdrqa_raw, aes(x = Time2)) + 
  geom_histogram(aes(x=Time2,y=..density..), binwidth = 2, color = "black", 
                 fill = IE2, show.legend = FALSE) +
  geom_density(aes(x=Time2,y=..density..),lwd = .7, colour = "black",
               fill = IE2, alpha = 0.4) +
  xlab('Time') +
  ylab('Density') +
  ggtitle("Distribution of Time") +
  theme_grey(base_size = 24)
ggsave('./results/figures/exp_3-histogram_time.png', height = 8, width = 10)

```

### Post-hoc

```{r H1-H3-posthoc, echo=FALSE}

# post-hoc of IE*TD2
posthoc.ie.td <- (emmeans(completion.model.raw, list(pairwise ~ TD*IE), adjust = "tukey"))[2]
posthoc.ie.td.df <- as.data.frame(posthoc.ie.td)
# add significance stars
stars <- as.data.frame(stars.pval(posthoc.ie.td.df[,6]))
posthoc.ie.td.df <- cbind(posthoc.ie.td.df, stars)
# rename columns
colnames(posthoc.ie.td.df) <- c("Pairwise Comparison", "Estimate", "Std. Error", "DF", "t-value", "Adjusted p-value", " ")
posthoc.ie.td.df <- posthoc.ie.td.df %>% mutate_if(is.numeric, round, digits=3) %>% select(-DF)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(posthoc.ie.td.df, caption = "p < .10, * p < .05, ** p < .001")

```

## Hypothesis 4: 
H4: Dyads in the restricted communication and bi-directional task switching condition (Condition 3) will engage in the most in-phase and anti-phase coordination. 

### Model

```{r H4-model, each=FALSE, echo = FALSE}

# raw model
coordination.model.raw = lmer(Determinism ~ 
                                # fixed effects
                                TD*IE*COM*Round +
                                # random effects of dyad
                                (1 | dyad),
                              data = mdrqa_raw, REML = FALSE)
pander_lme(coordination.model.raw,stats.caption = TRUE)
tab_model(coordination.model.raw)

# find residual DF for effect size calculation
summary(coordination.model.raw) # gives df.resid
df.residual = df.residual(coordination.model.raw)

# check out effect sizes
effectsizes_H4 <- as.data.frame(t_to_eta2(t = c(2.053, -2.624, 2.558),
                                          df_error = c(df.residual,df.residual,
                                                       df.residual)))

# build the effect size table
colnames(effectsizes_H4) <- c("Partial Eta2", "CI", "CI Low" , "CI High" )
effectsizes_H4 <- effectsizes_H4 %>% mutate_if(is.numeric, round, digits=3) %>%
  select(-CI) %>%
  mutate(Predictor = c("IE2:COM1","TD3:IE2:COM1","TD3:IE2:COM1:Round")) %>%
  relocate(Predictor)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")
# build table
pander(effectsizes_H4, caption = "")

```

### Plots

```{r H4-plots}

# interaction between IE and COM
ggplot(mdrqa_raw) +
  aes(x = IE, y = Determinism, fill = IE) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
  scale_fill_manual(values = IEcolors) + # magma
  theme_grey(base_size = 14) +
  ggtitle("Determism by IE and COM") +
  xlab('Individual Effectivities')
ggsave("./results/figures/exp_3-H4-plot_IExCOM.png", height = 5, width = 7)

# interaction between TD and IE
ggplot(mdrqa_raw) +
  aes(x = TD, y = Determinism, fill = TD) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~IE, labeller = as_labeller(c("1"='IE 1', "2"='IE 2', "3"='IE 3'))) +
  scale_fill_manual(values = TDcolors) + # magma
  theme_grey(base_size = 14) +
  ggtitle("Determism by TD and IE") +
  xlab('Task Demand')
ggsave("./results/figures/exp_3-H4-plot_TDxIE.png", height = 5, width = 7)

# # interaction between TD, IE, and COM
# ggplot(mdrqa_raw) +
#   aes(x = TD, y = Determinism, fill = TD) +
#   geom_boxplot() +
#   scale_fill_manual(values = TDcolors) + # magma
#   facet_grid(COM~IE, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"), IE = c('1'="IE 1", '2'="IE 2", '3'="IE 3"))) +
#   theme_grey(base_size = 14) +
#   ggtitle("Determism by TD, IE, and COM") +
#   xlab('Task Demand')
# ggsave("./results/figures/exp_3-H4-boxplot_TDxIExCOM.png", height = 5, width = 7)
# 
# # look at Time-Determinism relationship for TD and COM
# ggplot(mdrqa_raw) +
#   aes(x = Time, y = Determinism, color = TD) +
#   geom_point() +
#   scale_color_manual(values = TDcolors) + # magma
#   facet_grid(~COM, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
#   theme_grey(base_size = 14) +
#   ggtitle("Scatter of Time-Determinism Relationship by TD and COM") +
#   xlab('Time')
# ggsave("./results/figures/exp_3-H4-plot_scatter_TDxCOM.png", height = 5, width = 7)
# 
# # look at Time-Determinism relationship for TD and IE
# ggplot(mdrqa_raw) +
#   aes(x = Time, y = Determinism, color = TD) +
#   geom_point() +
#   scale_color_manual(values = TDcolors) + # magma
#   facet_grid(~IE, labeller = labeller(IE = c('1'="IE 1", '2'="IE 2", '3'="IE 3"))) +
#   theme_grey(base_size = 14) +
#   ggtitle("Scatter of Time-Determinism Relationship by TD and IE") +
#   xlab('Time')
# ggsave("./results/figures/exp_3-H4-plot_scatter_TDxIE.png")

# look at Time-Determinism relationship for IE and COM
ggplot(mdrqa_raw) +
  aes(x = Time, y = Determinism, fill = IE) +
  geom_point(colour = "black", pch=21, size = 2.5) +
  scale_fill_manual(values = IEcolors) + 
  facet_grid(~COM, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
  theme_grey(base_size = 16) +
  xlab('Task Completion Time') +
  scale_x_continuous(breaks=c(3.0, 3.8, 4.5))
ggsave("./results/figures/exp_3-H4-plot_scatter_IExCOM.png", height = 6, width = 8)

```

### Post-hoc

```{r H4-posthoc, echo=FALSE}

# post-hoc of IE*TD
posthoc.ie.td <- (emmeans(coordination.model.raw, list(pairwise ~ TD*IE), adjust = "tukey"))[2]
posthoc.ie.td.df <- as.data.frame(posthoc.ie.td)
# add significance stars
stars <- as.data.frame(stars.pval(posthoc.ie.td.df[,6]))
posthoc.ie.td.df <- cbind(posthoc.ie.td.df, stars)
# rename columns
colnames(posthoc.ie.td.df) <- c("Pairwise Comparison", "Estimate", "Std. Error", "DF", "t-value", "Adjusted p-value", " ")
posthoc.ie.td.df <- posthoc.ie.td.df %>% mutate_if(is.numeric, round, digits=3)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(posthoc.ie.td.df, caption = "p < .10, * p < .05, ** p < .001")

```

## Hypothesis 6-7: Whole-team synchrony
H6: Player-team and whole team synchrony will be strongest in the constrained communication condition. 
H7: Player-team and whole team synchrony will be strongest in the bi-directional task switching condition. 

### Model

```{r H6-H7-teamsync-model, echo = FALSE}

# raw model
whole.team.model.raw = lmer(scale(mean_team_sync) ~ 
                            TD*IE*COM*scale(Round) +
                             (1 |Dyad),
                           data=wide_raw, REML=FALSE)
pander_lme(whole.team.model.raw, stats.caption = FALSE)
#tab_model(whole.team.model.raw)

# find residual DF for effect size calculation
summary(whole.team.model.raw) # gives df.resid
df.residual = df.residual(whole.team.model.raw) 

# check out effect sizes
effectsizes_H6_H7 <- as.data.frame(t_to_eta2(t = c(2.222 , 2.357),
                                             df_error = c(df.residual,df.residual)))

# build the effect size table
colnames(effectsizes_H6_H7) <- c("Partial Eta2", "CI", "CI Low" , "CI High" )
effectsizes_H6_H7 <- effectsizes_H6_H7 %>% mutate_if(is.numeric, round, digits=3) %>% 
  select(-CI) %>%
  mutate(Predictor = c("TD2:IE2:Round", "TD3:IE2:Round")) %>%
  relocate(Predictor)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")
# build table
pander(effectsizes_H6_H7, caption = "")

```

### Plots

```{r H6-H7-teamsync-plots, echo = FALSE}

# # effect of TD
# ggplot(wide_raw) +
#   aes(x=TD, y=scale(mean_team_sync), fill = TD) + 
#   geom_boxplot(show.legend = FALSE) +
#   scale_fill_manual(values = TDcolors) +
#   #ggtitle("Impact of Task Demand on Team Synchrony") +
#   theme_grey(base_size = 12) +
#   xlab('Task Demand') +
#   ylab('Whole Team Synchrony')
# ggsave("./results/figures/exp_3-teamsync-plot_TD.png")
# 
# # interaction between TD and IE
# ggplot(wide_raw) +
#   aes(x = TD, y = scale(mean_team_sync), fill = TD) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_wrap(~IE, labeller = as_labeller(c("1"='IE 1', "2"='IE 2', "3"='IE 3'))) +
#   scale_fill_manual(values = TDcolors) + # magma
#   #ggtitle("Impact of Task Demand and Individual Effectivities on Team Synchrony") +
#   theme_grey(base_size = 14) +
#   xlab('Task Demand') +
#   ylab('Whole Team Synchrony')
# ggsave("./results/figures/exp_3-teamsync-plot_TDxIE.png")

# interaction between TD, IE, and Round
ggplot(wide_raw) +
  aes(x = as.factor(Round), y = scale(mean_team_sync), fill = as.factor(Round)) +
  geom_boxplot() +
  #scale_fill_manual(values = TDcolors) + # magma
  facet_grid(TD~IE, labeller = labeller(TD = c('1'="TD 1", '2'="TD 2", '3'="TD 3"), IE = c('1'="IE 1", '2'="IE 2", '3'="IE 3"))) +
  theme_grey(base_size = 14) +
  ggtitle("Whole team synchrony by TD, IE, and Round") +
  xlab('Round') +
  ylab('Whole Team Synchrony')
ggsave("./results/figures/exp_3-teamsync-boxplot_TDxIExRound.png", height = 5, width = 7)


```

### Post-hoc

```{r H6-H7-teamsync-posthoc, echo=FALSE}

# none needed

```

## Hypothesis 6-8: Player-team synchrony
H6: Player-team and whole team synchrony will be strongest in the constrained communication condition. 
H7: Player-team and whole team synchrony will be strongest in the bi-directional task switching condition (Condition 3). 
H8: Player-team synchrony will be highest for those in the role of P2 during the unidirectional task switching condition (Condition 2).

### Model

```{r H6-H7-H8-model, echo = FALSE}

# raw model
player.team.model.raw = lmer(scale(deg_player_sync) ~ TD*IE*COM*PlayerType*scale(Round) +
                              (1 | Dyad),
                            data=long_raw, REML=FALSE)
pander_lme(player.team.model.raw, stats.caption = FALSE)
#tab_model(player.team.model.raw)

# find residual DF for effect size calculation
summary(player.team.model.raw) # gives df.resid
df.residual = df.residual(player.team.model.raw) 

# check out effect sizes
effectsizes_H6_H8 <- as.data.frame(t_to_eta2(t = c(-2.754 , -3.119, 1.976,  3.278 , 2.291, 
                                                   2.922, 2.028, -2.596, -2.755, -3.219, 
                                                   -2.314, 2.537, -2.751, -1.982),
                                             df_error = c(df.residual,df.residual,
                                                          df.residual,df.residual,
                                                          df.residual,df.residual,
                                                          df.residual,df.residual,
                                                          df.residual,df.residual,
                                                          df.residual,df.residual,
                                                          df.residual,df.residual)))

# build the effect size table
colnames(effectsizes_H6_H8) <- c("Partial Eta2", "CI", "CI Low" , "CI High" )
effectsizes_H6_H8 <- effectsizes_H6_H8 %>% mutate_if(is.numeric, round, digits=3) %>% 
  select(-CI) %>%
  mutate(Predictor = c("IE2", "PlayerType2", "TD3:IE2",
                       "IE2:COM1", "IE2:COM3", "IE2:PlayerType2", "COM1:PlayerType2",
                       "TD3:IE2:COM3", "TD3:IE2:PlayerType2", "IE2:COM1:PlayerType2",
                       "IE2:COM3:PlayerType2", "TD3:IE2:COM3:PlayerType2", "TD2:IE2:COM1:PlayerType2:Round", 
                       "TD2:IE3:COM1:PlayerType2:Round")) %>%
  relocate(Predictor)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")
# build table
pander(effectsizes_H6_H8, caption = "")

```

### Plots

```{r H6-H7-H8-plots, each=FALSE}

# # interaction between TD and IE
# ggplot(long_raw) +
#   aes(x = TD, y = scale(deg_player_sync), fill = TD) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_wrap(~IE, labeller = as_labeller(c("1"='IE 1', "2"='IE 2', "3"='IE 3'))) +
#   scale_fill_manual(values = TDcolors) + # magma
#   theme_grey(base_size = 16) +
#   xlab('Task Demand')
# ggsave("./results/figures/exp_3-playersync-plot_TDxIE.png")
# 
# # interaction between COM and IE
# ggplot(long_raw) +
#   aes(x = IE, y = scale(deg_player_sync), fill = IE) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
#   scale_fill_manual(values = IEcolors) + # magma
#   theme_grey(base_size = 14) +
#   xlab('Individual Effectivities')
# ggsave("./results/figures/exp_3-playersync-plot_IExCOM.png")
# 
# # interaction between TD and COM
# ggplot(long_raw) +
#   aes(x = TD, y = scale(deg_player_sync), fill = TD) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
#   scale_fill_manual(values = TDcolors) + # magma
#   theme_grey(base_size = 14) +
#   xlab('Task Demand')
# ggsave("./results/figures/exp_3-playersync-plot_TDxCOM.png")

# interaction between COM and player type
ggplot(long_raw) +
  aes(x = COM, y = scale(deg_player_sync), fill = COM) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~PlayerType, labeller = as_labeller(c("1"='Restricted', "2"='Free'))) +
  scale_fill_manual(values = TDcolors) + # magma
  theme_grey(base_size = 14) +
  xlab('Communication Condition')
ggsave("./results/figures/exp_3-playersync-plot_COMxPlayerType.png")

# interaction between TD and player type
ggplot(long_raw) +
  aes(x = TD, y = scale(deg_player_sync), fill = TD) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~PlayerType, labeller = as_labeller(c("1"='Restricted', "2"='Free'))) +
  scale_fill_manual(values = TDcolors) + # magma
  theme_grey(base_size = 14) +
  xlab('Task Demand')
ggsave("./results/figures/exp_3-playersync-plot_TDxPlayerType.png")

# interaction between IE and player type
ggplot(long_raw) +
  aes(x = IE, y = scale(deg_player_sync), fill = IE) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~PlayerType, labeller = as_labeller(c("1"='Restricted', "2"='Free'))) +
  scale_fill_manual(values = IEcolors) +
  theme_grey(base_size = 14) +
  xlab('Individual Effectivities') +
  ylab('Player-Team Synchrony')
ggsave("./results/figures/exp_3-playersync-plot_IExPlayerType.png", height = 5, width = 7)

# interaction between player type, TD, and IE
ggplot(long_raw) +
  aes(x = TD, y = scale(deg_player_sync), fill = TD) +
  geom_boxplot(show.legend = FALSE) +
  facet_grid(PlayerType~IE, 
             labeller = labeller(PlayerType = c('1'="P1", '2'="P2"), 
                                 IE = c('1'="IE 1", '2'="IE 2", '3'="IE 3"))) +
  scale_fill_manual(values = TDcolors) + # magma
  theme_grey(base_size = 14) +
  xlab('Task Demand') +
  ylab('Player-Team Synchrony')
ggsave("./results/figures/exp_3-playersync-plot_TDxIExPlayerType.png", height = 5, width = 7)

# # interaction between player type, TD, and COM
# ggplot(long_raw) +
#   aes(x = TD, y = scale(deg_player_sync), fill = TD) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_grid(PlayerType~COM, 
#              labeller = labeller(PlayerType = c('1'="P1", '2'="P2"),
#                                  COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
#   scale_fill_manual(values = TDcolors) + # magma
#   theme_grey(base_size = 14) +
#   xlab('Task Demand')
# ggsave("./results/figures/exp_3-playersync-plot_TDxCOMxPlayerType.png")
# 
# # interaction between player type, IE, and COM
# ggplot(long_raw) +
#   aes(x = IE, y = scale(deg_player_sync), fill = IE) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_grid(PlayerType~COM,
#              labeller = labeller(PlayerType = c('1'="P1", '2'="P2"),
#                                  COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
#   scale_fill_manual(values = IEcolors) +
#   theme_grey(base_size = 14) +
#   xlab('Individual Effectivities')
# ggsave("./results/figures/exp_3-playersync-plot_IExCOMxPlayerType.png")
# 
# # interaction between player type, IE, TD, and COM
# ggplot(long_raw) +
#   aes(x = TD, y = scale(deg_player_sync), fill = IE) +
#   geom_boxplot(show.legend = TRUE) +
#   facet_grid(PlayerType~COM, 
#              labeller = labeller(PlayerType = c('1'="P1", '2'="P2"),
#                                  COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
#   scale_fill_manual(values = IEcolors) + 
#   theme_grey(base_size = 14) +
#   xlab('Task Demand') +
#   ylab('Whole Team Synchrony')
# ggsave("./results/figures/exp_3-playersync-plot_TDxCOMxPlayerTypexIE.png")
# 
# # look at Time-Determinism relationship for TD and COM
# ggplot(long_raw) +
#   aes(x = Time, y = deg_player_sync, color = TD) +
#   geom_point() +
#   scale_color_manual(values = TDcolors) + # magma
#   facet_grid(~COM, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
#   theme_grey(base_size = 14) +
#   ggtitle("Scatter of Time-Determinism Relationship by TD and COM") +
#   xlab('Time') +
#   ylab('Player-Team Synchrony')
# ggsave("./results/figures/exp_3-H4-plot_scatter_TDxCOM.png", height = 5, width = 7)

# look at Time-Determinism relationship for IE, COM, and player type
ggplot(long_raw) +
  aes(x = log(Time), y = scale(deg_player_sync), fill = IE) +
  geom_point(colour = "black", pch=21, size = 2) +
  scale_fill_manual(values = IEcolors) + # magma
  facet_grid(PlayerType~COM, labeller = labeller(PlayerType = c('1' = "P1", '2' = "P2"), COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
  theme_grey(base_size = 14) +
  xlab('Task Completion Time') +
  ylab('Player-Team Synchrony')
ggsave("./results/figures/exp_3-H4-plot_scatter_IExCOMxPlayerType.png", height = 5, width = 7)

# look at Time-Determinism relationship for TD, COM, and player type
ggplot(long_raw) +
  aes(x = log(Time), y = scale(deg_player_sync), color = TD) +
  geom_point() +
  scale_color_manual(values = TDcolors) + # magma
  facet_grid(PlayerType~COM, labeller = labeller(PlayerType = c('1' = "P1", '2' = "P2"), COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
  theme_grey(base_size = 14) +
  xlab('Task Completion Time') +
  ylab('Player-Team Synchrony') +
  scale_x_continuous(breaks=c(3.0, 3.8, 4.5))
ggsave("./results/figures/exp_3-H4-plot_scatter_TDxCOMxPlayerType.png", height = 5, width = 7)

# look at Time-PlayerTeamSync relationship for IE and COM
ggplot(long_raw) +
  aes(x = log(Time), y = scale(deg_player_sync), fill = IE) +
  geom_point(colour = "black", pch=21, size = 2) +
  scale_fill_manual(values = IEcolors) + 
  facet_grid(~COM, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
  theme_grey(base_size = 16) +
  xlab('Task Completion Time') +
  ylab('Player-Team Synchronization') +
  scale_x_continuous(breaks=c(3.0, 3.8, 4.5))
ggsave("./results/figures/exp_3-playerteam-plot_scatter_IExCOM.png", height = 6, width = 8)

```

### Post-hoc: TD*PlayerType

```{r H6-H7-H8-posthoc, echo=FALSE}

# post-hoc of PlayerType*TD
posthoc.td.pt <- (emmeans(player.team.model.raw, list(pairwise ~ TD*PlayerType), adjust = "tukey"))[2]
posthoc.td.pt.df <- as.data.frame(posthoc.td.pt)
# add significance stars
stars <- as.data.frame(stars.pval(posthoc.td.pt.df[,6]))
posthoc.td.pt.df <- cbind(posthoc.td.pt.df, stars)
# rename columns
colnames(posthoc.td.pt.df) <- c("Pairwise Comparison", "Estimate", "Std. Error", "DF", "t-value", "Adjusted p-value", " ")
posthoc.td.pt.df <- posthoc.td.pt.df %>% mutate_if(is.numeric, round, digits=3)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(posthoc.td.pt.df, caption = "p < .10, * p < .05, ** p < .001")

```

## Post-hoc: Det-Time comparisons across Exp 2 and 3

```{r exp2-exp3-det-time-comparisons, echo = FALSE}

exp2_data = read.table('../exp_2/data/mdrqa_and_conditions.csv', 
                       sep=',', header = TRUE)

# create factors and rename variables
exp2_data = exp2_data %>%
  mutate(dyad = as.factor(dyad)) %>%
  mutate(td_condition = as.factor(td_condition)) %>%
  mutate(ie_condition = as.factor(ie_condition)) %>%
  mutate(com_condition = as.factor(com_condition)) %>%
  rename(TD = td_condition) %>% 
  rename(IE = ie_condition) %>% 
  rename(Determinism = DET) %>% 
  rename(Time = timer) %>% 
  rename(Dyad = dyad) %>% 
  rename(Round = round_number) %>%
  rename(COM = com_condition)

# check out average round completion times and average determinism times
exp2_det_time <- exp2_data %>%
  select(Dyad, Round, TD, IE, COM, Determinism, Time)
exp2_det_time$Experiment = as.factor(2)
exp3_det_time <- mdrqa_raw %>%
  select(Dyad, Round, TD, IE, COM, Determinism, Time2) %>%
  rename(Time = Time2)
exp3_det_time$Experiment = as.factor(3)

# run t-tests to see if they were significantly different
all_data <- rbind(exp2_det_time, exp3_det_time)
res.time <- var.test(log(Time) ~ Experiment, data = all_data)
t.test.time <- t.test(log(Time) ~ Experiment, data = all_data)
summary(t.test.time)
t.test.time.desc = all_data %>% 
  group_by(Experiment) %>% summarise(mean = mean(Time), sd = sd(Time))

# test for differences in determinism
res.det <- var.test(Determinism ~ Experiment, data = all_data)
t.test.det <- t.test(Determinism ~ Experiment, data = all_data)
summary(t.test.det)
t.test.det.desc = all_data %>% 
  group_by(Experiment) %>% summarise(mean = mean(Determinism), sd = sd(Determinism))
# test for differences in variability
levene.det <- leveneTest(Determinism ~ Experiment, data = all_data)

```

### Post-hoc: Variability of COM across IE conditions

``` {r post-hoc-variability}

# subset the data
data_COM12_IE1 <- mdrqa_raw %>% filter(COM == "1" | COM == "2") %>% filter(IE == "1")
data_COM12_IE3 <- mdrqa_raw %>% filter(COM == "1" | COM == "2") %>% filter(IE == "3")
data_COM23_IE1 <- mdrqa_raw %>% filter(COM == "2" | COM == "3") %>% filter(IE == "1")
data_COM23_IE3 <- mdrqa_raw %>% filter(COM == "2" | COM == "3") %>% filter(IE == "3")

# look at differences in IE variabiltiy between COM1 and COM2
levene.com12.ie1 <- leveneTest(Determinism ~ COM, data = data_COM12_IE1)
levene.com12.ie3 <- leveneTest(Determinism ~ COM, data = data_COM12_IE3)
levene.com23.ie1 <- leveneTest(Determinism ~ COM, data = data_COM23_IE1)
levene.com23.ie3 <- leveneTest(Determinism ~ COM, data = data_COM23_IE3)


# subset the data by TD (across players)
data_COM12_TD2 <- long_raw %>% filter(COM == "1" | COM == "2") %>% filter(TD == "2")
data_COM23_TD2 <- long_raw %>% filter(COM == "2" | COM == "3") %>% filter(TD == "2")
levene.com12.td2 <- leveneTest(deg_player_sync ~ COM, data = data_COM12_TD2)
levene.com23.td2 <- leveneTest(deg_player_sync ~ COM, data = data_COM23_TD2)

```