---
title: "5-LMEM"
output:
  word_document: default
  html_document: default
date: "2023-04-26"
---

This Rmd runs inferential statistics and builds plots for Experiment 2.

# Set up and data cleaning

```{r setup, include=FALSE}

# clear workspace and load packages
rm(list=ls())
#setwd("./Documents/github/division-of-labor-analyses/exp_2")
source("../required_packages.R")
source("../libraries_and_functions.R")

# read in data
data = read.table('./data/mdrqa_and_conditions.csv', 
                       sep=',', header = TRUE)

# create factors and rename variables
data = data %>%
  mutate(dyad = as.factor(dyad)) %>%
  mutate(td_condition = as.factor(td_condition)) %>%
  mutate(ie_condition = as.factor(ie_condition)) %>%
  mutate(com_condition = as.factor(com_condition)) %>%
  rename(TD = td_condition) %>% 
  rename(IE = ie_condition) %>% 
  rename(Determinism = DET) %>% 
  rename(Time = timer) %>% 
  mutate(Time2 = Time) %>%
  rename(Dyad = dyad) %>% 
  rename(Round = round_number) %>%
  rename(COM = com_condition)

# change contrasts for COM such that COM2 is the reference condition
contrasts(data$COM) = contr.treatment(3, base = 2)

# specify global plotting variables for TD: magma pallete
TD1 = "#fcfdbf"
TD2 = "#fc8961" 
TD3 = "#b73779"
TDcolors = c(TD1, TD2, TD3)
# specify global plotting variables for IE: viridis pallete
IE1 = "#fde725"
IE2 = "#21918c"
IE3 = "#3b528b"
IEcolors = c(IE1, IE2, IE3)

```

## Hypothesis 1-3: 
(1) Dyads in the restricted communication condition (COM2) will perform better than those in the no and free communication groups. 
(2) Those in the no (COM1) and free (COM3) communication groups will perform similarly. 
(3) Dyads in the restricted communication (COM2) and bi-directional task switching condition (IE 3) will outperform all other groups.

### Model

```{r H1-H3-model, echo=FALSE}

###### 2. Construct the model for H1-H3 ######

# check on normality of Time
shapiro.test(data$Time)
shapiro.test(log(data$Time)) # still not > .05, but more normal.
shapiro.test(scale(data$Time))

# take log of time
data <- data %>% mutate(Time = log(Time))

# raw model
completion.model.raw = lmer(Time ~ 
              # fixed effects
              TD*IE*COM + Round +
              # random effects of dyad
              (1 | Dyad),
            data = data, REML = FALSE)
pander_lme(completion.model.raw,stats.caption = TRUE)
#tab_model(completion.model.raw)

# find residual DF for effect size calculation
summary(completion.model.raw)
df.residual = df.residual(completion.model.raw)

# check out effect sizes
effectsizes_H1_H3 <- as.data.frame(t_to_eta2(t = c(2.948, -3.874, 1.970, 2.006, -2.019),
                                          df_error = c(df.residual, 
                                                       df.residual, 
                                                       df.residual,
                                                       df.residual,
                                                       df.residual)))

# build the effect size table
colnames(effectsizes_H1_H3) <- c("Partial Eta2", "CI", "CI Low" , "CI High" )
effectsizes_H1_H3 <- effectsizes_H1_H3 %>% mutate_if(is.numeric, round, digits=3) %>% 
  select(-CI) %>%
  mutate(Predictor = c("TD2", "Round", "TD2:COM1", "IE2:COM3", "TD2:IE2:COM3")) %>%
  relocate(Predictor)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")
# build table
pander(effectsizes_H1_H3, caption = "")

```

### Post-hoc: TDxIE

```{r H1-H3-posthoc, echo=FALSE}

# post-hoc of TD*IE
posthoc.com.td <- (emmeans(completion.model.raw, list(pairwise ~ TD*IE), adjust = "tukey"))[2]
posthoc.com.td.df <- as.data.frame(posthoc.com.td)
# add significance stars
stars <- as.data.frame(stars.pval(posthoc.com.td.df[,6]))
posthoc.com.td.df <- cbind(posthoc.com.td.df, stars)
# rename columns
colnames(posthoc.com.td.df) <- c("Pairwise Comparison", "Estimate", "Std. Error", "DF", "t-value", "Adjusted p-value", " ")
posthoc.com.td.df <- posthoc.com.td.df %>% mutate_if(is.numeric, round, digits=3) %>% select(-DF)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(posthoc.com.td.df, caption = "")

```

### Plots

```{r H1-H3-plots, each=FALSE, echo=FALSE}

# # effect of TD
# ggplot(data, aes(x=TD, y=Time, fill = TD)) + 
#   geom_boxplot(show.legend = FALSE) +
#   scale_fill_manual(values = TDcolors) +
#   ggtitle("Impact of Task Demand on Time") +
#   theme_grey(base_size = 12) +
#   xlab('Task Demand') +
#   ylab('Task Completion Time')
# ggsave("./results/figures/exp_2-H1-H2-TD.png")
# 
# # effect of COM
# ggplot(data, aes(x=COM, y=Time, fill = COM)) + 
#   geom_boxplot(show.legend = FALSE) +
#   scale_fill_manual(values = IEcolors) +
#   theme_grey(base_size = 12) +
#   xlab('Communication')
# ggsave("./results/figures/exp_2-H1-H2-plot_COM.png")
# 
# # interaction between IE and COM
# ggplot(data) +
#   aes(x = IE, y = Time, fill = IE) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
#   scale_fill_manual(values = IEcolors) + # magma
#   theme_grey(base_size = 14) +
#   xlab('Individual Effectivities') +
#   ylab('Task Completion Time')
# ggsave("./results/figures/exp_2-H1-H2-plot_IExCOM.png", width = 7, height = 5)

# interaction between TD and COM
ggplot(data) +
  aes(x = TD, y = Time, fill = TD) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
  scale_fill_manual(values = TDcolors) + # magma
  theme_grey(base_size = 14) +
  xlab('Task Demand') +
  ylab('Task Completion Time')
ggsave("./results/figures/exp_2-H1-plot_TDxCOM.png", width = 7, height = 5)

# # interaction between TD and Round
# ggplot(data) +
#   aes(x = as.factor(Round), y = Time, fill = as.factor(Round)) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_wrap(~TD, labeller = as_labeller(c("1"='TD 1', "2"='TD 2', "3"='TD 3'))) +
#   scale_fill_viridis(discrete = TRUE, option = "rocket") +
#   ggtitle("Impact of Task Demand and Round on Time") +
#   theme_grey(base_size = 12) +
#   labs(fill = "Round") +
#   xlab('Round')
# ggsave("./results/figures/exp_1-H2-plot_TDxIExRound.png")

# interaction between TD, IE, and COM
ggplot(data) +
  aes(x = TD, y = Time, fill = TD) +
  geom_boxplot(show.legend = FALSE) +
  facet_grid(COM~IE, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"), IE = c('1'="IE 1", '2'="IE 2", '3'="IE 3"))) +
  scale_fill_manual(values = TDcolors) + # magma
  ggtitle("Impact of TD, IE, and COM on Time") +
  theme_grey(base_size = 14) +
  xlab('Task Demand') +
  ylab('Task Completion Time')
ggsave("./results/figures/exp_2-H1-H3-plot_TDxIEXCOM.png", width = 7, height = 5)

# # effect of Round
# ggplot(data) +
#   aes(x = as.factor(Round), y = Time2, fill = as.factor(Round)) +
#   geom_boxplot(show.legend = FALSE) +
#   scale_fill_viridis(discrete = TRUE, option = "rocket") +
#   ggtitle("Impact of Round on Time") +
#   theme_grey(base_size = 12) +
#   labs(fill = "Round") +
#   xlab('Round') +
#   ylab('Time')
# ggsave("./results/figures/exp_1-H2-plot_TDxIExRound.png")

```

### Post-hoc: Variability of IE

```{r post-hoc-variability}
# test for difference in variability for 
data_IE1 <- data %>% filter(IE == "1")
data_IE2 <- data %>% filter(IE == "2")
data_IE3 <- data %>% filter(IE == "3")

# run levene's tests
levene.ie1.td <- leveneTest(Time ~ TD, data = data_IE1)
levene.ie2.td <- leveneTest(Time ~ TD, data = data_IE2)
levene.ie3.td <- leveneTest(Time ~ TD, data = data_IE3)


```

## Hypothesis 4: 
(4) Dyads in the restricted communication (COM2) and bi-directional task switching condition (IE1) will engage in the most coordination. 

### Model

```{r H4-model, each=FALSE}

# raw model
coordination.model.raw = lmer(Determinism ~ 
               # fixed effects
               TD*IE*COM*Round +
               # random effects of dyad
               (1 | Dyad),
             data = data, REML = FALSE)
pander_lme(coordination.model.raw,stats.caption = TRUE)
#tab_model(coordination.model.raw)

# find residual DF for effect size calculation
summary(coordination.model.raw) # gives df.resid
df.residual = df.residual(coordination.model.raw) 

# check out effect sizes
effectsizes_H4 <- as.data.frame(t_to_eta2(t = c(-2.944, 2.293, 2.710, 2.384, 2.895,
                                                3.534, 2.762, -2.086, 2.423, -3.241,
                                                -2.614, -3.319, -2.933, -2.240, -2.524,
                                                -2.710, -2.790, -3.422, 2.737, 2.879,
                                                1.973, 2.774, 3.272),
                                          df_error = c(df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual,df.residual,
                                                       df.residual)))

# build the effect size table
colnames(effectsizes_H4) <- c("Partial Eta2", "CI", "CI Low" , "CI High" )
effectsizes_H4 <- effectsizes_H4 %>% mutate_if(is.numeric, round, digits=3) %>% 
  select(-CI) %>%
  mutate(Predictor = c("TD3", "Round", "TD3:IE2", "TD3:IE3", "TD3:COM1", 
                       "TD3:COM3", "TD3:Round", "IE2:Round", "COM3:Round", 
                       "TD3:IE2:COM1", "TD3:IE3:COM1", "TD3:IE2:COM3", "TD3:IE3:COM3", "TD3:IE2:Round",
                       "TD3:IE3:Round", "TD3:COM1:Round", "TD2:COM3:Round", "TD3:COM3:Round",
                       "TD3:IE2:COM1:Round", "TD3:IE3:COM1:Round", "TD2:IE2:COM3:Round",
                       "TD3:IE2:COM3:Round", "TD3:IE3:COM3:Round")) %>%
  relocate(Predictor)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")
# build table
pander(effectsizes_H4, caption = "")

```

### Post-hoc: TD*IE

```{r H4-posthoc, echo = FALSE}

# post-hoc of IE*TD
posthoc.ie.td <- (emmeans(completion.model.raw, list(pairwise ~ TD*IE), adjust = "tukey"))[2]
posthoc.ie.td.df <- as.data.frame(posthoc.ie.td)
# add significance stars
stars <- as.data.frame(stars.pval(posthoc.ie.td.df[,6]))
posthoc.ie.td.df <- cbind(posthoc.ie.td.df, stars)
# rename columns
colnames(posthoc.ie.td.df) <- c("Pairwise Comparison", "Estimate", "Std. Error", "DF", "t-value", "Adjusted p-value", " ")
posthoc.ie.td.df <- posthoc.ie.td.df %>% mutate_if(is.numeric, round, digits=3) %>% select(-DF)

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(posthoc.ie.td.df, caption = "")

```

### Plots

```{r H4-plots, each=FALSE}

# # effect of TD
# ggplot(data, aes(x = TD, y = Determinism, fill = TD)) + 
#   geom_boxplot(show.legend = FALSE) +
#   scale_fill_manual(values = TDcolors) +
#   xlab('Task Demand') +
#   ggtitle("Determism by TD") +
#   theme_grey(base_size = 14) 
# ggsave('./results/figures/exp_2-H4-TD_collapsed.png')
# 
# # effect of COM
# ggplot(data, aes(x = COM, y = Determinism, fill = COM)) + 
#   geom_boxplot(show.legend = FALSE) +
#   scale_fill_manual(values = TDcolors) +
#   xlab('Communication') +
#   ggtitle("Determism by COM") +
#   theme_grey(base_size = 14) 
# ggsave('./results/figures/exp_2-H4-COM_collapsed.png')
# 
# # effect of IE
# ggplot(data, aes(x = IE, y = Determinism, fill = IE)) +
#   geom_boxplot(show.legend = FALSE) +
#   scale_fill_manual(values = IEcolors) +
#   xlab('Individual Effectivities') +
#   ggtitle("Determism by IE") +
#   theme_grey(base_size = 14)
# ggsave('./results/figures/exp_2-H4-IE_collapsed.png')

# interaction between TD and IE
ggplot(data) +
  aes(x = TD, y = Determinism, fill = TD) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~IE, labeller = as_labeller(c("1"='IE 1', "2"='IE 2', "3"='IE 3'))) +
  scale_fill_manual(values = TDcolors) + # magma
  theme_grey(base_size = 14) +
  xlab('Task Demand')
ggsave("./results/figures/exp_2-H4-plot_TDxIE.png", width = 5, height = 5)

# # interaction between TD and COM
# ggplot(data) +
#   aes(x = TD, y = Determinism, fill = TD) +
#   geom_boxplot(show.legend = FALSE) +
#   facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
#   scale_fill_manual(values = TDcolors) + # magma
#   theme_grey(base_size = 14) +
#   ggtitle("Determism by TD and COM") +
#   xlab('Task Demand')
# ggsave("./results/figures/exp_2-H4-plot_TDxCOM.png")

# interaction between IE and COM
ggplot(data) +
  aes(x = IE, y = Determinism, fill = IE) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
  scale_fill_manual(values = IEcolors) + # magma
  theme_grey(base_size = 14) +
  ggtitle("Determism by IE and COM") +
  xlab('Individual Effectivities')
ggsave("./results/figures/exp_2-H4-plot_IExCOM.png")

# # interaction between TD, IE, and COM
# ggplot(data) +
#   aes(x = TD, y = Determinism, fill = TD) +
#   geom_boxplot() +
#   scale_fill_manual(values = TDcolors) + # magma
#   facet_grid(COM~IE, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"), 
#                                          IE = c('1'="IE 1", '2'="IE 2", '3'="IE 3"))) +
#   theme_grey(base_size = 14) +
#   ggtitle("Determism by TD, IE, and COM") +
#   xlab('Task Demand')
# ggsave("./results/figures/exp_2-H4-boxplot_TDxIExCOM.png")
# 
# # look at Time-Determinism relationship for TD and COM
# ggplot(data) +
#   aes(x = Time2, y = Determinism, color = TD) +
#   geom_point() +
#   scale_color_manual(values = TDcolors) + # magma
#   facet_grid(~COM, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
#   theme_grey(base_size = 14) +
#   ggtitle("Scatter of Time-Determinism Relationship by TD and COM") +
#   xlab('Time')
# ggsave("./results/figures/exp_2-H4-plot_scatter_TDxCOM.png")

# look at Time-Determinism relationship for IE and COM
ggplot(data) +
  aes(x = Time, y = Determinism, fill = IE) +
  geom_point(colour = "black", pch=21, size = 2) +
  #scale_color_manual(values = IEcolors) + # magma
  scale_fill_manual(values = c("1" = "#fde725", "2" = "#21918c", "3" = "#3b528b")) + # magma
  facet_grid(~COM, labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
  theme_grey(base_size = 16) +
  #ggtitle("Scatter of Time-Determinism Relationship by TD and COM") +
  xlab('Task Completion Time')
ggsave("./results/figures/exp_2-H4-plot_scatter_IExCOM.png", height = 6, width = 8)

# # look at Time-Determinism relationship for TD and IE
# ggplot(data) +
#   aes(x = Time2, y = Determinism, color = TD) +
#   geom_point() +
#   scale_color_manual(values = TDcolors) + # magma
#   facet_grid(~IE, labeller = labeller(IE = c('1'="IE 1", '2'="IE 2", '3'="IE 3"))) +
#   theme_grey(base_size = 14) +
#   ggtitle("Scatter of Time-Determinism Relationship by TD and IE") +
#   xlab('Time')
# ggsave("./results/figures/exp_2-H4-plot_scatter_TDxIE.png")

# look at Time for TD and COM across rounds
ggplot(data) +
  aes(x = Round, y = Time2, color = TD) +
  geom_point(alpha = .4) +
  #geom_smooth() +
  geom_smooth(method = 'lm', se = FALSE) +
  scale_color_manual(values = TDcolors) + # magma
  facet_grid(~COM,labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
  theme_grey(base_size = 16) +
  xlab('Round') +
  ylab('Task Completion Time') +
  ylim(c(43, 100))
ggsave("./results/figures/exp_2-H4-plot_scatter_COMxTDxRound.png", height = 6, width = 7)

# # look at Time for IE and COM across rounds
# ggplot(data) +
#   aes(x = Round, y = Time2, color = IE) +
#   geom_point(alpha = .4) +
#   #geom_smooth() +
#   geom_smooth(method = 'lm', se = FALSE) +
#   scale_color_manual(values = IEcolors) + # magma
#   facet_grid(~COM,labeller = labeller(COM = c('1'="COM 1", '2'="COM 2", '3'="COM 3"))) +
#   theme_grey(base_size = 16) +
#   #ggtitle("Scatter of Time-Determinism Relationship by TD and COM") +
#   xlab('Round') +
#   ylab('Completion Time') +
#   ylim(c(43, 100))
# ggsave("./results/figures/exp_2-H4-plot_scatter_COMxIExRound.png", height = 6, width = 7)

```

```{r additional-plots}

TD1 = "#fcfdbf"
TD2 = "#fc8961" 
TD3 = "#b73779"
TDcolors = c(TD1, TD2, TD3)
# specify global plotting variables for IE: viridis pallete
IE1 = "#fde725"
IE2 = "#21918c"
IE3 = "#3b528b"

# plot histograms by TD*IE collapsed across dyads
ggplot(data) + 
  geom_histogram(aes(x=Time2,y=..density..), binwidth = 2, color = "black", 
                 fill = IE2, show.legend = FALSE) +
  geom_density(aes(x=Time2,y=..density..),lwd = .7, colour = "black",
               fill = IE2, alpha = 0.4) +
  xlab('Task Completion Time') +
  ylab('Density') +
  ggtitle("Distribution of Time") +
  theme_grey(base_size = 24)
ggsave('./results/figures/exp_2-histogram_time.png', height = 8, width = 10)

```

### Post-hoc: Variability of COM

``` {r post-hoc-variability}

# test for difference in variability for 
data_IE1 <- data %>% filter(IE == "1")
data_IE3 <- data %>% filter(IE == "3")
data_TD2 <- data %>% filter(TD == "2")

# COM2-by-IE1 and both COM1-by-IE1 and COM3-by-IE1
levene.ie1 <- leveneTest(Determinism ~ COM, data = data_IE1)

# COM2-by-IE3 and both COM1-by-IE3 and COM3-by-IE3
levene.ie3 <- leveneTest(Determinism ~ COM, data = data_IE3)

# COM2-by-IE3 and both COM1-by-IE3 and COM3-by-IE3
levene.td2 <- leveneTest(Determinism ~ COM, data = data_TD2)

# specify global plotting variables for COM
COM1 = "#0d0887"
COM2 = "#7e03a8"
COM3 = "#cc4778"
COMcolors = c(COM1, COM2, COM3)

# plot the differences
ggplot(data_IE1) +
  aes(x = COM, y = Determinism, fill = COM) +
  geom_boxplot(show.legend = FALSE, notch  = FALSE) +
  #facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
  scale_fill_manual(values = COMcolors) + # magma
  theme_grey(base_size = 14) +
  #ggtitle("Determism by IE and COM") +
  xlab('Communication')

# plot the differences
ggplot(data_TD2) +
  aes(x = COM, y = Determinism, fill = COM) +
  geom_boxplot(show.legend = FALSE, notch  = FALSE) +
  #facet_wrap(~COM, labeller = as_labeller(c("1"='COM 1', "2"='COM 2', "3"='COM 3'))) +
  scale_fill_manual(values = COMcolors) + # magma
  theme_grey(base_size = 14) +
  #ggtitle("Determism by IE and COM") +
  xlab('Communication')

```